PACE 2024: OCMu64, reductions and a branch-and-bound solver for\\ One-sided Crossing Minimization

### 2024-09-03 tex/poster.tex
Fix small typos.

        \textbf{The lamma is optimal:}
        Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$.
        Assuming there exists vertices $m$ in between $a$ and $b$, $l$ left of $\min
        N(v)$ and $r$ right of $\max N(u)$ \ragnar{Is this strong enough? Do $u$ and $v$
          need reversing? Or should we just say left of the min and right of the max
          of the two?}, there exists some \emph{weighted} distribution $X$ over
        $\{l, m, r\}$ such that $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, so that
        $v$ may have to go before $u$.

>>>>

        \textbf{The lemma is optimal:}
        Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$.
        Assuming there exist vertices $m$ in between $a$ and $b$, $l$ left of $\min
        N(v)$ and $r$ right of $\max N(u)$ \ragnar{Is this strong enough? Do $u$ and $v$
          need reversing? Or should we just say left of the min and right of the max
          of the two?}, there exists some \emph{weighted} distribution $X$ over
        $\{l, m, r\}$ such that $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, so that
        $v$ may have to go before $u$.
